---
title: "Assignment 4"
author: "Shude Guo"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### 1.	Heart Start produces automated external defibrillators (AEDs) in each of two different plants (A and B). The unit production costs and monthly production capacity of the two plants are indicated in the table below. The AEDs are sold through three wholesalers. The shipping cost from each plant to the warehouse of each wholesaler along with the monthly demand from each wholesaler are also indicated in the table. How many AEDs should be produced in each plant, and how should they be distributed to each of the three wholesaler warehouses so as to minimize the combined cost of production and shipping?

#### * Let Xij = the number of AEDs produced in plant i and then sent to the warehouses j, i=1,2; j=1,2,3.

```
/* Objective function */
min: 622 x11 + 614 x12 + 630 x13 + 641 x21 + 645 x22 + 649 x23;

/* Constraints */
x11 + x12 + x13 + x14 = 100;
x21 + x22 + x23 + x24 = 120;
x11 + x21 = 80;
x12 + x22 = 60;
x13 + x23 = 70;
x14 + x24 = 10;
```

```{r warning=FALSE}
library(lpSolveAPI)
```
```{r}
x <- read.lp("sguo5_4.1.lp")
```
```{r echo=TRUE}
solve(x)
```
```{r echo=TRUE}
get.objective(x)
```
```{r echo=TRUE}
get.variables(x)
```
